\normalfont{disCOVIDer19}

### 2020-04-02 Documentation/article_4.tex
Update

\paragraph{Background} \label{Background}
In December 2019 different cases of pneumonia were reported in Wuhan (China) \cite{huang2020clinical}. Their origin was later ascribed to a new virus classified as \textit{Severe acute respiratory syndrome coronavirus 2} (SARS-CoV-2) whose TEM and SEM pictures are reported in the Fig. \ref{coronavirus_picture} The origin of this virus is still subject of scientific debate between the scientific community, however one of the most common opinion is that this virus comes from bats, in particular the genus Rhinolophus \cite{zhou2020pneumonia}. The most compelling feature of this virus is that is its ability to spread also via coughing and sneezing \cite{ghinai2020first}, and also by touching infected surfaces \cite{chang2020protecting}. Differently with respect to the SARS-CoV the virus seems to have a lower mortality rate \cite{sorensen2006severe,weiss2020clinical}.

@@

>>>>

\subsection{Background} \label{Background}
In December 2019 different cases of pneumonia were reported in Wuhan (China) \cite{huang2020clinical}. Their origin was later ascribed to a new virus classified as \textit{Severe acute respiratory syndrome coronavirus 2} (SARS-CoV-2) whose TEM and SEM pictures are reported in the Fig. \ref{coronavirus_picture} The origin of this virus is still subject of scientific debate between the scientific community, however one of the most common opinion is that this virus comes from bats, in particular the genus Rhinolophus \cite{zhou2020pneumonia}. The most compelling feature of this virus is that is its ability to spread also via coughing and sneezing \cite{ghinai2020first}, and also by touching infected surfaces \cite{chang2020protecting}. Differently with respect to the SARS-CoV the virus seems to have a lower mortality rate \cite{sorensen2006severe,weiss2020clinical}.

@@

\subsection{Historical Background}

In the last centuries different cases of pandemic diseases were recorded: from our point of view the dynamics of them it is useful to understand, ad perhaps to model,  that further peaks may succeed the first one also with a highest death rate.

\paragraph{The  deadliest pandemics in human history: the Spanish flu}

 The first one, the biggest one known for humans (in terms of spread as well for deaths \cite{potter2001history} ), is the Spanish Flu: this name is quite misleading since it was not originated in Spain, but the Spanish newspaper were the first one to talk about because large part of the involved countries were involved in the Great War (1914-1918). The origin of this disease is still under research: some scholars focused on the  United States \cite{crosby_2003,barry2004site}on France \cite{shanks2016no} and on Asia \cite{langford2005did}.  The disease was ascribed to the virus A/H1N1 a subtype of influenza A Virus. The spread of the disease was strongly amplified by the fact that many people lived very close in to a very difficult hygienic conditions. As one can see from Fig. \ref{SpanishFLU} there are basically three waves: the initial spread, the second wave and the third wave. The second wave, that is the most lethal one, coincides with the end of the war and with the coming back of the troops: the close contact inside the trains, and the diffusion of the troops inside their home villages/cities increased abruptly the contagion rate and then the death rate. Furthermore this effect was amplified by the fact that a more deadly mutation of the virus diffused  \cite{barry2008cross}. As pointed out by different scholars such effect was enhanced since, the infected people, for which the severity of the ill was higher were transferred by train  into the hospitals and so  the virus spread with a higher rate \cite{wever2014death}.As it is possible to note from Fig. \ref{Mortality_spanish_flu} this second wave was largely more deadly for young people with respect the first wave. Finally, as can be noted in the plot \ref{SpanishFLU}, a third wave also manifested in the beginning of 1919: in this case the mortality was higher with respect to the first one but lower to the second one. In the end this pandemic infected 500 million people and a large part of them , from 17 to 50 million, died \cite{spreeuwenberg2018reassessing}. It is worth nothing that, just to give a comparison, the causalities in the Great War were from 8.8 to 10.7 million among soldiers and 11 million among civilian \cite{haythornthwaite1996world}

\begin{figure}[h]
 \centering
 \includegraphics[width=1\linewidth]{Figures/SpanishFLU.png} 
 \caption{Pneumonia and Influenza mortality from 1910-1922 in London: note the tree peaks due to the spanish flu. In the in box the variation of the diffusion rate R$_{0}$ is reported. Image taken from \cite{he2011mechanistic} }
 \label{SpanishFLU}
\end{figure}

\begin{figure}[h]
 \centering
 \includegraphics[width=0.6\linewidth]{Figures/Mortality_spanish_flu.png} 
 \caption{Morthality range distribution for the two waves of Spanish flu: note that the second one was more severe for the young people. Image taken from \cite{taubenberger20061918}}
 \label{Mortality_spanish_flu}
\end{figure}
